\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{tikz}
\usepackage{float}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, backgrounds, calc}

% --- TikZ common styles ---
\tikzset{
  stageblock/.style={rectangle, rounded corners=5pt, draw=black!70, fill=blue!12,
    text width=5.5em, minimum height=2.4em, align=center, font=\small\bfseries},
  reportblock/.style={rectangle, rounded corners=3pt, draw=black!50, fill=yellow!18,
    text width=5em, minimum height=2em, align=center, font=\small},
  gateblock/.style={diamond, aspect=2.2, draw=black!70, fill=orange!22,
    text width=4.5em, minimum height=2em, align=center, font=\small},
  svcblock/.style={rectangle, rounded corners=4pt, draw=teal!70, fill=teal!10,
    text width=5em, minimum height=2.2em, align=center, font=\small},
  engblock/.style={rectangle, rounded corners=4pt, draw=purple!70, fill=purple!10,
    text width=6.5em, minimum height=2.2em, align=center, font=\small},
  termblock/.style={rectangle, rounded corners=10pt, draw=gray!70, fill=gray!15,
    text width=5em, minimum height=2em, align=center, font=\small},
  arrow/.style={-{Stealth[length=5pt]}, thick},
  dasharrow/.style={-{Stealth[length=4pt]}, thick, dashed, gray!70},
  groupbox/.style={draw=gray!50, dashed, rounded corners=6pt, fill=gray!5, inner sep=8pt}
}

\title{A Practical 20-Minute Security Baseline Chain for Node.js Services}
\author{Security Claw Project}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
This document summarizes a practical security analysis workflow designed for Node.js services such as OpenClaw and NanoClaw. The workflow prioritizes common, widely adopted tools and enforces a strict 20-minute execution budget. We describe the chain design, implementation hardening decisions, and measured outcomes from local experiments.
\end{abstract}

\section{Problem Statement}
Many teams need a reproducible baseline security check that is fast enough to run in pull requests and frequent CI jobs. Our objective is to build a minimal but effective scan chain that can:
\begin{itemize}[leftmargin=1.5em]
  \item detect dependency vulnerabilities,
  \item detect risky code patterns,
  \item detect container and repository misconfigurations,
  \item complete within 1200 seconds.
\end{itemize}

\section{Security Chain Design}
The baseline chain consists of three sequential stages:
\begin{enumerate}[leftmargin=1.5em]
  \item \textbf{Dependency scan}: \texttt{npm audit --audit-level=high --json}
  \item \textbf{SAST scan}: \texttt{semgrep scan --config p/default --json}
  \item \textbf{Container and misconfiguration scan}: \texttt{trivy fs --scanners vuln,misconfig --severity HIGH,CRITICAL --format json}
\end{enumerate}

To support reuse across similar services, stage commands are configured through service profiles (JSON) and executed by a shared engine script.

Figure~\ref{fig:pipeline} illustrates the sequential execution flow of the three-stage chain.

\begin{figure}[H]
\centering
\begin{tikzpicture}[
  node distance=1.1cm and 1.4cm
]
  % Stage nodes
  \node[termblock] (start) {Start};
  \node[stageblock, right=of start] (dep) {Stage 1\\npm audit};
  \node[stageblock, right=of dep]   (sast) {Stage 2\\Semgrep};
  \node[stageblock, right=of sast]  (cont) {Stage 3\\Trivy};
  \node[termblock,  right=of cont]  (done) {Summary\\JSON};

  % Report nodes below each stage
  \node[reportblock, below=0.8cm of dep]  (r1) {npm-audit\\*.json};
  \node[reportblock, below=0.8cm of sast] (r2) {semgrep\\*.json};
  \node[reportblock, below=0.8cm of cont] (r3) {trivy\\*.json};

  % Main flow arrows
  \draw[arrow] (start) -- (dep);
  \draw[arrow] (dep)   -- (sast);
  \draw[arrow] (sast)  -- (cont);
  \draw[arrow] (cont)  -- (done);

  % Report dashed arrows
  \draw[dasharrow] (dep)  -- (r1);
  \draw[dasharrow] (sast) -- (r2);
  \draw[dasharrow] (cont) -- (r3);

  % Budget label
  \node[above=0.5cm of sast, font=\small\itshape, gray] {Budget: 1200 s};
\end{tikzpicture}
\caption{Three-stage baseline security scan chain.}
\label{fig:pipeline}
\end{figure}

\section{Implementation and Hardening}
The framework includes:
\begin{itemize}[leftmargin=1.5em]
  \item service profiles under \texttt{services/*.json},
  \item execution scripts under \texttt{engine/},
  \item CI workflows under \texttt{.github/workflows/}.
\end{itemize}

Figure~\ref{fig:arch} shows how the shared engine layer decouples service-specific configuration from scan execution.

\begin{figure}[H]
\centering
\begin{tikzpicture}[
  node distance=0.9cm and 1.2cm
]
  % Service profile column
  \node[svcblock] (nc) {NanoClaw\\profile};
  \node[svcblock, below=0.7cm of nc] (oc) {OpenClaw\\profile};
  \node[svcblock, below=0.7cm of oc] (cx) {Custom\\profile};

  % Engine
  \node[engblock, right=1.8cm of oc] (eng) {Engine\\run-chain.sh};

  % Output reports
  \node[reportblock, right=1.8cm of eng, yshift=1.1cm]  (rn) {npm audit\\report};
  \node[reportblock, right=1.8cm of eng]                (rs) {Semgrep\\report};
  \node[reportblock, right=1.8cm of eng, yshift=-1.1cm] (rt) {Trivy\\report};

  % Policy gate
  \node[gateblock, right=1.5cm of rs] (gate) {Policy\\Gate};

  % Arrows: profiles to engine
  \draw[arrow] (nc) -- (eng);
  \draw[arrow] (oc) -- (eng);
  \draw[arrow] (cx) -- (eng);

  % Arrows: engine to reports
  \draw[arrow] (eng) -- (rn);
  \draw[arrow] (eng) -- (rs);
  \draw[arrow] (eng) -- (rt);

  % Arrows: reports to gate
  \draw[arrow] (rn) -- (gate);
  \draw[arrow] (rs) -- (gate);
  \draw[arrow] (rt) -- (gate);

  % Group boxes
  \begin{scope}[on background layer]
    \node[groupbox, fit=(nc)(oc)(cx), label=above:{\small Service Profiles}] {};
    \node[groupbox, fit=(rn)(rs)(rt), label=above:{\small Reports}] {};
  \end{scope}
\end{tikzpicture}
\caption{Multi-service framework architecture: service profiles → engine → reports → policy gate.}
\label{fig:arch}
\end{figure}

Key hardening decisions:
\begin{itemize}[leftmargin=1.5em]
  \item replace string-based shell execution with structured \texttt{command + args} invocation,
  \item avoid direct unsafe interpolation in workflow \texttt{run} blocks,
  \item preserve before/after comparison for patch validation through summary diffs.
\end{itemize}

\section{Experimental Setup}
\textbf{Target}: NanoClaw local repository.\\
\textbf{Budget}: 1200 seconds.\\
\textbf{Outputs}: JSON reports and summarized metrics.

\section{Measured Results}
Two representative runs were recorded:

\begin{table}[h]
\centering
\begin{tabular}{lcccc}
\toprule
Run Label & Elapsed (s) & npm audit (High/Critical) & Semgrep Findings & Trivy High/Critical \\
\midrule
exp2 & 7 & 0 / 0 & 49 & 3 \\
local\_framework\_test & 21 & 0 / 0 & 54 & 3 (+1 misconfig) \\
\bottomrule
\end{tabular}
\caption{Observed baseline chain outcomes under the 20-minute budget.}
\end{table}

All observed runs completed far below the 1200-second limit.

\section{Patch Validation Flow}
For vulnerability remediation, the process includes:
\begin{enumerate}[leftmargin=1.5em]
  \item baseline scan and summary snapshot,
  \item patch application,
  \item re-scan with the same chain,
  \item summary diff and policy gate check.
\end{enumerate}

A patch is considered successful when targeted findings disappear in the after-state and no new High/Critical issues are introduced.

Figure~\ref{fig:patchflow} shows the before/after comparison workflow.

\begin{figure}[H]
\centering
\begin{tikzpicture}[
  node distance=0.85cm and 1.3cm
]
  % Before column
  \node[stageblock] (scan1) {Baseline\\Scan};
  \node[reportblock, below=of scan1] (sum1) {before/\\summary.json};

  % Patch
  \node[engblock, right=1.6cm of scan1] (patch) {Apply\\Patch};

  % After column
  \node[stageblock, right=1.6cm of patch] (scan2) {Re-run\\Scan};
  \node[reportblock, below=of scan2] (sum2) {after/\\summary.json};

  % Diff
  \node[engblock, below=1.4cm of patch] (diff) {compare-\\before-after.sh};

  % Gate
  \node[gateblock, below=of diff] (gate) {Policy\\Gate};

  % Pass/Fail
  \node[termblock, right=1.3cm of gate] (pass) {\textcolor{green!60!black}{PASS}};
  \node[termblock, left=1.3cm of gate]  (fail) {\textcolor{red!70!black}{FAIL}};

  % Arrows
  \draw[arrow] (scan1) -- (sum1);
  \draw[arrow] (scan1) -- (patch);
  \draw[arrow] (patch) -- (scan2);
  \draw[arrow] (scan2) -- (sum2);
  \draw[arrow] (sum1)  -- (diff);
  \draw[arrow] (sum2)  -- (diff);
  \draw[arrow] (diff)  -- (gate);
  \draw[arrow] (gate)  -- node[above, font=\tiny]{no new H/C} (pass);
  \draw[arrow] (gate)  -- node[above, font=\tiny]{regression} (fail);
\end{tikzpicture}
\caption{Patch validation flow: before/after scan comparison and policy gate.}
\label{fig:patchflow}
\end{figure}

\section{Limitations}
\begin{itemize}[leftmargin=1.5em]
  \item Semgrep findings include both true positives and rule-noise; triage is required.
  \item Vulnerability presence in dependencies may require upstream package updates, not only local code changes.
  \item Results can vary with tool database update time.
\end{itemize}

\section{Conclusion}
This work demonstrates that a minimal, reusable, and hardened security chain can provide meaningful baseline coverage for Node.js services within strict CI time constraints. The approach is practical for continuous monitoring and can be extended with service-specific policy gates and patch regression checks.

\end{document}
